### 2025-07-10 paper/quarto_aaai/paper.tex
adjusted caption

\caption{\label{fig-mnist}Explanations for \emph{MNIST} for BL (top) and
CT (bottom). First columns is a randomly chosen factual 0. Columns 2
through 5 are \emph{ECCo} counterfactuals for that factual in target
classes 1 to 4. Columns 6 trough 10 show integrated gradients averaged
over all test images in the corresponding classes (5-9).}

>>>>

\caption{\label{fig-mnist}Explanations for \emph{MNIST} for BL (top) and
CT (bottom). First column is a random factual 0. Columns 2 to 5 are
corresponding \emph{ECCo} counterfactuals in target classes 1 to 4.
Columns 6 to 10 show integrated gradients averaged over all test images
in classes 5 to 9.}

### 2025-07-10 paper/sections/experiments.qmd
adjusted caption

![Explanations for *MNIST* for BL (top) and CT (bottom). First columns is a randomly chosen factual 0. Columns 2 through 5 are *ECCo* counterfactuals for that factual in target classes 1 to 4. Columns 6 trough 10 show integrated gradients averaged over all test images in the corresponding classes (5-9).](/paper/figures/mnist_body.png){#fig-mnist}

>>>>

![Explanations for *MNIST* for BL (top) and CT (bottom). First column is a random factual 0. Columns 2 to 5 are corresponding *ECCo* counterfactuals in target classes 1 to 4. Columns 6 to 10 show integrated gradients averaged over all test images in classes 5 to 9.](/paper/figures/mnist_body.png){#fig-mnist}
